---
title: "Aerosol Sense"
output: html_notebook
---

```{r}
library(aod)
library(ggplot2)
library(tidyverse)
library(caret)
```
Data had been cleaned:
  - MRN changed to Unit##
  - Collection Time changed to include only Date
  - Result only reflects Positive = 1, all other results of Neg, Inc, Inv = 0.
```{r}
aero <- read.csv("C:/Users/t.ganz/Desktop/AeroSense/Aero_02.csv")
aero$Collection <- as.Date(aero$Collection, "%m/%d/%Y")
aero$Unit <- factor(aero$Unit)
head(aero)
```
-----Data Viz-----
Pos Counts for All Units
```{r}
ggplot(aero,aes(Collection, Result))+
  geom_col()+
  ylim(0,6)+
  scale_x_date(limits = as.Date(c("2021-05-01","2022-05-01")))+
  ggtitle("All Units")+
  theme_bw()+
  theme(plot.title = element_text(size=16))
```
Pos Counts per Unit
```{r}
for (i in c(1:10)){
  a <- subset(aero, Unit == i)
  b <- ggplot(a, aes(Collection, Result))+
    geom_col()+
    ylim(0,3)+
    scale_x_date(limits = as.Date(c("2021-05-01","2022-05-01")))+
    ggtitle("Unit",i)+
    theme_bw()+
    theme(plot.title = element_text(size=16))
  print(b)
}
```


```{r}
summary(aero)
```

```{r}
xtabs(~Result + Unit, data=aero)
```
Logistic Regression ---
- the models only unit (Collection Time has been left out)
```{r}
aero_logit <- glm(Result~Unit, data=aero, family = "binomial")
```

```{r}
summary(aero_logit)
```
Analysis---

- formula:  p = exp(-1.9459 + 0.2283*Unit2 - 1.2993*Unit3 - 0.3802*Unit4 + 0.1804*Unit5 - 
11.6202*Unit6 - 1.7430*Unit7 + 1.6205*Unit8 + 2.100*Unit9 + 0.7673*Unit10) / [1 + exp(-1.9459 + 0.2283*Unit2 - 1.2993*Unit3 - 0.3802*Unit4 + 0.1804*Unit5 - 11.6202*Unit6 - 1.7430*Unit7 + 1.6205*Unit8 + 2.100*Unit9 + 0.7673*Unit10)].

- Only Unit 9 shows significant coefficient
- Units 2, 5, 8, 9, and 10 have positive coefficients
- Units 3, 4, 6, and 7 have negative coefficients
- Unit 6 with one result is suspect
- Review Confidence Intervals using SE
```{r}
confint.default(aero_logit)
```
```{r}
newdata <- factor(sample(c(1:10), 819, replace = TRUE))
length(newdata)
probs <- predict(aero_logit, newdata=data.frame(Unit=newdata))
head(probs)
pred.class <- ifelse(probs > 0.5, "pos", "neg")
plot(newdata,pred.class)
```
```{r}
head(aero)
```

Wald's Test ---
```{r}
wald.test(b = coef(aero_logit), Sigma = vcov(aero_logit), Terms = 2:10)
```
Analysis---
- Wald's test/Chi square indicates unit is significant.
- 

```{r}
l <- cbind(0,0,0,0,0,0,0,0,1,0,-1)
wald.test(b = coef(aero_logit), Sigma = vcov(aero_logit), L = l)
```
---
NEW DATASETS
Aero_04 - 330 observations with additional features:
  - Location of Unit, Collection Start datetime, Collection End datetime
  - *note - missing times assumed 12 hours difference (n<20)
Aero_05 - 818 observations of original Aero_02 data with:
  - Location of Unit - assumed by mode of location assigned to unit from metadata
  - Metadata for units 8 and 9 included cleaned/dirty status not reflected in dataframe
  - Unit 6 removed - 
---
```{r}
aero4 <- read.csv("C:/Users/t.ganz/Desktop/AeroSense/Aero_04.csv")
aero4$Collection <- as.Date(aero4$Collection, "%m/%d/%Y")
aero4$Unit <- factor(aero4$Unit)
aero4$coll_st <- as.POSIXct(aero4$coll_st,format="%m/%d/%Y %H:%M")
aero4$coll_end <- as.POSIXct(aero4$coll_end,format="%m/%d/%Y %H:%M")
View(aero4)
```
Add column with length of collection time by finding difference between 
coll_end and coll_st - perform stats analysis.
```{r}
aero4$coll_span <- aero4$coll_end - aero4$coll_st
```
coll_span column contains length of collection time in minutes
```{r}
aero4$coll_span <- as.numeric(aero4$coll_span)
summary(aero4$coll_span)
```
```{r}
ggplot(aero4, aes(coll_span))+
  geom_histogram(binwidth = 20)+
  theme_bw()
```
remove outliers with spans > 2000 minutes
```{r}
which(aero4$coll_span >2000)
```
```{r}
aero4_1 <- aero4[-c(42, 43, 98, 99),]
summary(aero4_1$coll_span)
```

```{r}
ggplot(aero4_1, aes(coll_span))+
  geom_histogram(binwidth = 10)+
  theme_bw()
```
Histogram of collection times per Unit...
```{r}
for (i in c(1:5,7:10)){
  a <- subset(aero4_1, Unit == i)
  b <- ggplot(a, aes(coll_span))+
    geom_histogram(binwidth = 10)+
    ggtitle("Unit",i)+
    theme_bw()
  print(b)
}
```
Summary stats for collection times for all units:
```{r}
for (i in c(1:5,7:10)){
  a <- subset(aero4_1, Unit == i)
  b <- summary(a$coll_span)
  print(b)
}
```
```{r}
xtabs(~Result + Unit, data=aero4_1)
```
```{r}
unique(aero4_1$Location)
```

 Regression per Unit
```{r}
for (i in c(1:5,7:10)){
  a <- subset(aero4_1, Unit == i)
  b <- glm(Result~coll_span, data=a, family = binomial)
  print(summary(b))
}
```

```{r}
for (i in c(1:5,7:10)){
  a <- subset(aero4_1, Unit == i)
  b <- plot(Result~coll_span, data=a)
  b
}
```
```{r}
plot(coll_span~Unit, data=aero4_1)
```
Both the regressions and the scatter plots indicate no relationship

Log Transformation?
```{r}
aero4_1$log_span <- log(aero4_1$coll_span)
```
```{r}
for (i in c(1:5,7:10)){
  a <- subset(aero4_1, Unit == i)
  b <- plot(Result~log_span, data=a)
  b
}
```
Box-Cox Transformation?
```{r}
aero4_1$box_span <- boxcox(aero4_1$coll_span)
```


```{r}
```





```{r}
aa <- subset(aero4_1, Unit == 5)
aa
new_span <- data.frame(coll_span = c(1:max(aa$coll_span)))
new_span
model <- glm(Result~coll_span, data=aa, family = binomial)
summary(model)
probs_4 <- model %>% predict(new_span, type = "response")
probs_4
pred_4.class <- ifelse(probs_4 > 0.5, "pos", "neg")
pred_4.class

aa %>%
  mutate(prob = ifelse(pred_4.class == "pos", 1, 0)) %>%
  ggplot(aes(coll_span, prob)) +
  geom_point(alpha = 0.2) +
  geom_smooth(method = "glm", method.args = list(family = "binomial")) +
  labs(
    title = "Logistic Regression Model", 
    x = "collection span",
    y = "Probability of detecting pos"
    )
```


```{r}
data.frame(c(20,180))
```


```{r}
```

